---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rlibproj

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/paleolimbot/rlibproj/workflows/R-CMD-check/badge.svg)](https://github.com/paleolimbot/rlibproj/actions)
[![Codecov test coverage](https://codecov.io/gh/paleolimbot/rlibproj/branch/master/graph/badge.svg)](https://codecov.io/gh/paleolimbot/rlibproj?branch=master)
<!-- badges: end -->

The goal of rlibproj is to provide a literal wrapper around the PROJ C API. It uses [libproj](https://github.com/paleolimbot/libproj) as a standalone copy of PROJ independent of a system installation.

## Installation

You can install the development version from [R Universe](https://r-universe.dev/) with:

``` r
install.packages("libproj", repos = "https://paleolimbot.r-universe.dev")
```

## Example

Create a transform and transform some coordinates:

```{r example}
library(rlibproj)
pipe <- proj_create_crs_to_crs("OGC:CRS84", "EPSG:3827")
proj_trans(pipe, proj_coord(-64, 45))
```

You can transform arbitrary R objects using the [crs2crs interface](https://github.com/paleolimbot/crs2crs):

```{r}
library(crs2crs)
crs_set_engine(crs_engine_rlibproj())

library(sf)
nc <- read_sf(system.file("shape/nc.shp", package = "sf"))

nc %>% 
  crs_set_longlat(datum = "NAD27") %>% 
  crs_transform("EPSG:3857")
```
